Graphics

### 2018-09-10 contest/graphics/graphics.Rmd
add graphs for points and games won

---
title: "Graphics"
author: "Kayla Frisoli, Shannon Gallagher, and Amanda Luby"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = TRUE)
library(deuce)
library(dplyr)
library(ggplot2)
library(forcats)
library(stringr)
library(knitr)
library(kableExtra)
library(pander)

@@

@@

>>>>

---
title: "Graphics"
author: "We have no names"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = TRUE)
library(deuce)
library(dplyr)
library(ggplot2)
library(forcats)
library(stringr)
library(knitr)
library(kableExtra)
library(pander)
library(gridExtra)

@@

# Univariate distributions

## Points won

```{r, fig.height=4, fig.width=12}
p1 <- ggplot(gs_players) + geom_histogram(aes(pointswon), bins=40) + 
  labs(x = "Winner points")

p2 <- ggplot(gs_players) + geom_density(aes(pointswon, color = tournament)) + 
  labs(x = "Winner points")

p3 <- ggplot(gs_players) + geom_density(aes(pointswon, color = league))+ 
  labs(x = "Winner points")

grid.arrange(p1, p2, p3, ncol=3, widths=c(.25, .41, .34))

```{r, fig.height=3.5, fig.width=10, fig.align='center'}

p1 <- ggplot(gs) + geom_point(aes(w_pointswon, l_pointswon)) + 
  geom_abline(slope=1, intercept=0, color="red") + 
  labs(x = "Winner points", y = "Loser points")

p2 <- ggplot(gs) + geom_point(aes(w_pointswon, l_pointswon, color = league), alpha=.3) + 
    scale_color_manual(values=c("#339966", "#336699")) +
  geom_abline(slope=1, intercept=0, color="red") + 
  geom_smooth(aes(w_pointswon, l_pointswon, color = league), method='lm') + 
  labs(x = "Winner points", y = "Loser points")

grid.arrange(p1, p2, ncol=2, widths=c(.48, .52))

## Games won

```{r, fig.height=4, fig.width=10}

p1 <- ggplot(gs_players) + geom_histogram(aes(gameswon), bins=30)+ 
  labs(x = "Winner games")

p2 <- ggplot(gs_players) + geom_density(aes(gameswon, color = tournament))+ 
  labs(x = "Winner games")

p3 <- ggplot(gs_players) + geom_density(aes(gameswon, color = league))+ 
  labs(x = "Winner games")

grid.arrange(p1, p2, p3, ncol=3, widths=c(.25, .41, .34))

```{r, fig.height=4, fig.width=8, fig.align='center'}

p1 <- ggplot(gs) + geom_point(aes(w_gameswon, l_gameswon)) + 
  geom_abline(slope=1, intercept=0, color="red") + 
  labs(x = "Winner games", y = "Loser games")

p2 <- ggplot(gs) + geom_point(aes(w_gameswon, l_gameswon, color = league), alpha=.3) + 
    scale_color_manual(values=c("#339966", "#336699")) +
  geom_abline(slope=1, intercept=0, color="red") + 
  geom_smooth(aes(w_gameswon, l_gameswon, color = league), method='lm')  + 
  labs(x = "Winner games", y = "Loser games")

grid.arrange(p1, p2, ncol=2, widths=c(.48, .52))

@@

# MDS

```{r}
gs_num <- select(gs, w_ace, w_df, w_svpt, w_1stIn, w_1stWon, w_2ndWon,
                w_bpSaved, w_bpFaced) %>%
na.omit()

mds <- cmdscale(dist(scale(gs_num)), k = 2) %>%
  as.data.frame()  # default column names will be V1, V2

mds$tournament <- select(gs, w_ace, w_df, w_svpt, w_1stIn, w_1stWon, w_2ndWon,
                w_bpSaved, w_bpFaced, tournament) %>%
na.omit() %>% pull( tournament)

ggplot(mds, aes(V1, V2, label = tournament, color=tournament)) + geom_text()
```
